Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
added memory usages on the constrained cluster

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/success-rates-tiny}
        \caption{Success ratey by algorithm by workflow size. Taller is better. }
        \label{fig:success-rates-tiny}
        \vspace{-0.3cm}
    \end{figure}

>>>>

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/success-rates-tiny}
        \caption{Success rates by algorithm by workflow size. Taller is better. }
        \label{fig:success-rates-tiny}
        \vspace{-0.3cm}
    \end{figure}

    Memory usages on the constrained cluster are depicted in~Fig.~\ref{fig:memory-usage-constrained}.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/mem-usage-constrained-onlyvalid}
        \caption{Memory usage by different heuristics by workflow size.}
        \label{fig:memory-usage-constrained}
        \vspace{-0.3cm}
    \end{figure}
